Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-11-23 paper/main.tex
clean putative functions of PPA subregions

% posterior connectivity
The pPPA is more strongly functionally connected to the occipital visual cortex
\citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% functionality
The pPPA is functionally more responsive than aPPA to low-level features of
(abstract) objects or scenes \citep{baldassano2013differential,
nasr2014thinking, rajimehr2011parahippocampal}.

% anterior
The anterior PPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
objects (e.g. spatial contextual associations
\citep{aminoff2007parahippocampal, aminoff2015associative} and scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract identity/category
\citep{marchette2015outside, watson2016patterns}).

@@

data suggest that the PPA is not a ally homogeneous area buconsists of
submodules that ``activate selectively to scenes'' and ``cooperate to build a
complete representation of a scene'' \citep{baldassano2013differential}.

%
Our data suggest that PPA might contain identifiable subregions, but these
subregions should not be considered as completely independent modules.
%
Both subregions activate selectively to scenes, and the parahippocampal region
(at least in macaques) is densely self-connected (Suzuki 2009), implying that
these subregions cooperate to build a complete representation of a scene.
%
Their distinct connectivity properties, however, do suggest that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.

%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information \citep{baldassano2013differential}.
%
Previous work has shown that PPA responds to objects that have spatial
associations [Aminoff et al. 2007], are space-defining [Mullally and Maguire
2011], and are navigationally-relevant [Janzen and Van Turennout 2004].
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape. If anterior PPA is involved in processing
spatial context, then space-defining or navigationally-relevant objects could
activate anterior PPA more strongly than our abstract objects, which were
unfamiliar and provided no sense of context or orientation.
%
Further experiments will be required to determine whether what type of
object-related information is used in this region
\citep{baldassano2013differential}.

%
\citep{baldassano2016two}: We propose that scene processing is fundamentally
divided into two collaborating but distinct networks
%
One is focused on the visual features of a scene image. The other is related to
contextual retrieval and navigation.
%
Under this framework, scene perception is less the function of a unified set of
distributed neural machinery and more of ``an ongoing dialogue between the
material and symbolic aspects of the past and the continuously unfolding
present'' (Baker, 2012, in The Word Hoard).

%
\citep{baldassano2016two} with respect to natural scene perception: one can
imagine at least two separable functions:
%
1) processing the specific visual features present in the current glance of a
scene,
%
2) and connecting that to the stable, high-level knowledge of where the place
exists in the world, what has happened here in the past, and what possible
actions we could take here in the future \citep{baldassano2016two}.
%
For most cognitive and physical tasks we undertake in real-world places, the
specific visual attributes we perceive are just a means to this end, of
recalling and updating information about the physical environment; ``the
essential feature of a landmark is not its design, but the place it holds in a
city’s memory'' [Muschamp, 2006, in New York Times]\citep{baldassano2016two}.

\paragraph{contextual associations}

%
The PCH has been implicated in the integration and retrieval of contextual
associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
2008a, 2008b].
%
According to this view, activity in PHC reflects modality-independent retrieval
of contextual information from memory (contextual associations: relations
between objects and conditions that describe, represent, and bring meaning to an
environment; such as which objects typically occur in a given scene and where
they are likely to be located relative to one another; [Aminoff et al., 2013])
\citep{baumann2016functional}.

Results: aPHC is more active during contextual judgments regardless of stimulus
category (scenes vs objects) or modality (word vs picture)
\citep{baumann2016functional}.
%
The left aPHC was active in all contextual judgment task conditions. This
suggests a functional segregation, with posterior sections of the PHC supporting
visuospatial processing of scenes and anterior sections of the left PHC involved
in contextual associative processing\citep{baumann2016functional}.

%
Activation maxima associated with visuospatial and mnemonic
processes were spatially segregated, providing support for the existence of
functionally distinct subregions along the PHC longitudinal axis and suggesting
that the PHC serves as a functional interface between perception and memory
systems\citep{baumann2016functional}.

Results suggests a predominantly perceptual role for the pPHC and a mnemonic
role for the anterior parahippocampal cortex (Note: the anterior parahippocampal
cortex should not be confused with the anterior portion of the parahippocampal
gyrus, which includes the perirhinal cortex; Ranganath and Ritchey,
2012.)\citep{baumann2016functional}.

We suggest that the aPHC encodes incoming information in an amodal format and
acts as an interface with other memory regions, including the hippocampal,
retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,

@@

\citep{aminoff2015associative}: Three regions of the cortex that have bee
identified as responding selectively to visual scenes: the PHC/lingual region
(commonly referred to as the “parahippocampal place area”) [8–12]),
retrosplenial complex (including the retrosplenial cortex and portions of the
posterior cingulate and precuneus, RSC) [13–15]), and a lateral occipital region
termed the “occipital place area” (OPA; also referred to as the transverse
occipital sulcus, TOS) [16–18]).
%
All three of these brain regions are functionally defined by comparing the BOLD
signals–as measured by fMRI–arising from viewing scenes to those arising from
viewing objects or faces (e.g., [19])\citep{aminoff2015associative}.

% baldassano2016two
RSC: appears to be most directly involved in orienting the viewer to the
structure of the environment (both within and beyond the borders of the
presented image) for the purpose of navigational planning; it encodes both
absolute location and facing direction [Vass and Epstein, 2013; Epstein and
Vass, 2014; Marchette et al., 2014], integrates across views presented in a
panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
[Epstein et al., 2007a,b]\citep{baldassano2016two}.

% contrasting the two networks
Several previous studies have already shown differential effects within these
two networks. Contrasting the functional connectivity patterns of RSC versus OPA
or lateral occipital cortex (LOC; Nasr et al., 2013) or anterior versus
posterior PPA [Baldassano et al., 2013] show a division between the two
networks, consistent with our results. Contrasting scene-specific activity with
general (image or word) memory retrieval showed an anterior versus posterior
distinction in PPA and cIPL/OPA, with only more anterior regions (aPPA and cIPL,
along with RSC) responding to content-independent retrieval tasks [Johnson and
Rugg, 2007; Fairhall et al., 2014]\citep{baldassano2016two}.

@@

%
\citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
functional distinction between pPPA and OPA is currently unclear. Previous work
has speculated about the purpose of the apparent ventral and dorsal
``duplication'' of regions sensitive to large landmarks, proposing that it may
be related to different output goals (e.g., action planning in OPA, object
recognition in pPPA)[Konkle and Caramazza, 2013], or to different input
connections (e.g., lower visual field processing in OPA, upper visual field
processing in pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may
also use information from different visual eccentricities: OPA processing less
peripheral, relatively high-resolution environmental features. pPPA processing
more peripheral, large-scale geometry, and context [Baldassano et al.,
2016a] \citep{baldassano2016two}.

>>>>

% posterior connectivity
The pPPA is more strongly functionally connected to the occipital visual cortex
\citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% functionality
The pPPA is functionally more responsive than aPPA to low-level features of
scenes or (abstract) objects \citep{baldassano2013differential,
nasr2014thinking, rajimehr2011parahippocampal}.

% anterior
The anterior PPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).

\todo[inline]{the mother of total confusion: in Aminoff (2007, 2013): anterior
    PPA = spatial associations, region anterior to PPA = non-spatial
    associations; but in Aminoff (2015): posterior PPA = spatial associations
    and anterior PPA = non-spatial associations; hence: complete bullshit;
ignore Aminoff (2015) due to various reasons}

@@

The PPA is not a functionally homogeneous area but consists of
subregions that ``activate selectively to scenes'' and ``cooperate to build a
complete representation of a scene'' \citep{baldassano2013differential}.
%
Their distinct connectivity properties do suggest that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding \citep{baldassano2013differential}.

%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information \citep{baldassano2013differential}. Previous work has shown that PPA
responds to objects that have spatial associations [Aminoff et al. 2007], are
space-defining [Mullally and Maguire 2011], and are navigationally-relevant
[Janzen and Van Turennout 2004]. These types of responses require spatial memory
and cannot be based purely on visual features like object shape.
\citep{baldassano2013differential}.

%
[If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation.
%
Further experiments will be required to determine whether what type of
object-related information is used in this region
\citep{baldassano2013differential}.]

@@

% baldassano2016two
\citep{baldassano2016two}: RSC appears to be most directly
involved in orienting the viewer to the structure of the environment (both
within and beyond the borders of the presented image) for the purpose of
navigational planning; it encodes both absolute location and facing direction
[Vass and Epstein, 2013; Epstein and Vass, 2014; Marchette et al., 2014],
integrates across views presented in a panoramic sequence [Park and Chun, 2009],
and shows strong familiarity effects [Epstein et al., 2007a,b]
\citep{baldassano2016two}.

@@

%
\citep{baldassano2016two} regarding functional difference pPPA vs. OPA: The
functional distinction between pPPA and OPA is currently unclear. Previous work
has speculated about the purpose of the apparent ventral and dorsal
``duplication'' of regions sensitive to large landmarks, proposing that it may
be related to different output goals (e.g., action planning in OPA, object
recognition in pPPA)[Konkle and Caramazza, 2013], or to different input
connections (e.g., lower visual field processing in OPA, upper visual field
processing in pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may
also use information from different visual eccentricities: OPA processing less
peripheral, relatively high-resolution environmental features. pPPA processing
more peripheral, large-scale geometry, and context [Baldassano et al., 2016a]
\citep{baldassano2016two}.
